### 2016-10-19 IEEEtran/designConcept_GP.tex
minor changes in the intro and IV.B

(II) \textit{Energy data level and social level services:} These services are provided by the YouPower app and its backend. The design of the YouPower app (and its backend) consists of three self-contained composable parts: (A) \textit{House Cooperatives} (contextualized and deployed to the Stockholm test site); (B) \textit{Demand-Side Management} (contextualized and deployed
to the Trento test site); and (C) \textit{Action Suggestions} (contextualized and deployed to both test sites). They are discussed in Section~\ref{sect:design_concept}.

@@

This part of YouPower is designed for the Trento test site and can have wider application.
It provides users historical and quasi real-time consumption and production information, and facilitates users to leverage load elasticity in order to maximize self-consumption of rooftop PV productions. 
Energy data is displayed at appliances (if smart plugs are installed), household, and electricity consortia levels. %to inform users of their own energy consumption patterns and those in the neighborhood. 
%
Consumption at the appliance level enables users to gain deeper understanding of their daily actions and the resulting energy use. 
% 
Historical and current consumption and production at the household level allow users to compare those two and potentially maximize self-consumption. 
% 
Aggregated and average consumption at the consortia level informs users of neighborhood energy consumption and allows comparisons.  
% 
In addition, dynamic Time-of-Use (ToU) signals are displayed  to assist users in load shifting during their daily actions.

>>>>

(II) \textit{Energy data level and social level services:} These services are provided by the YouPower app and its back-end. The design of the YouPower app (and its back-end) consists of three self-contained composable parts: (A) \textit{House Cooperatives} (contextualized and deployed to the Stockholm test site); (B) \textit{Demand-Side Management} (contextualized and deployed
to the Trento test site); and (C) \textit{Action Suggestions} (contextualized and deployed to both test sites). They are discussed in Section~\ref{sect:design_concept}.

@@

This part of the YouPower app is designed for the Trento test site and can have wider application.
It provides users historical and quasi real-time consumption and production information, and facilitates users to leverage load elasticity in order to maximize self-consumption of rooftop PV productions. 
Energy data is displayed at appliances (if smart plugs are installed), household, and electricity consortia levels. %to inform users of their own energy consumption patterns and those in the neighborhood. 
%
Consumption at the appliance level enables users to gain deeper understanding of their daily actions and the resulting energy use. 
% 
Historical and current consumption and production at the household level allow users to compare those two and potentially maximize self-consumption. 
% 
Aggregated and average consumption at the consortia level informs users of neighborhood energy consumption and allows comparisons.  
% 
In addition, dynamic Time-of-Use (ToU) signals are displayed  to assist users in load shifting during their daily actions.

### 2016-10-19 IEEEtran/intro.tex
minor changes in the intro and IV.B

The research is performed within the framework of the EU FP7 CIVIS project. It has test sites in Stockholm (Sweden) and Trento (Italy) with domestic energy consumers. 
% 
In Sweden, those who buy a home officially own the right to inhabit the estate and must join a corresponding \textit{housing cooperative} 
that owns and maintains its estates. The test site in Stockholm is composed of sixteen(?) housing cooperatives, each of which has annually elected board members who make energy related decisions on behalf of the cooperative members. 
In the case of Trento test site, two local \textit{electricity consortia} are managing energy related issues. The consortia are particularity  interested in load shifting since the Trento households also have PV panel productions.  
This two types of communities are at the center of YouPower design. 
% 
The rest of this paper presents the design process of YouPower, gives an overview of the platform, and discuss in more detail its design concept.

>>>>

The research is performed within the framework of the EU FP7 CIVIS project. It has test sites in Stockholm (Sweden) and Trento (Italy) with domestic energy consumers. 
% 
In Sweden, those who buy a home officially own the right to inhabit the estate and must join a corresponding \textit{housing cooperative} 
that owns and maintains its estates. The test site in Stockholm is composed of \textbf{sixteen(?)} housing cooperatives, each of which has annually elected board members who make energy related decisions on behalf of the cooperative members. 
In the case of Trento test site, two local \textit{electricity consortia} produce and sell renewable (hydro and solar) energy to consortium members. Household rooftop PV panels are also common in this region.  The consortia are highly interested in load shifting to optimize the use of local renewables reducing dependency on the national supply. 
These two types of communities are at the center of YouPower design. 
% 
The rest of this paper presents the design process of YouPower, gives an overview of the platform, and discuss in more detail its design concept.
